comgen-outline

### 2017-06-10 paper/comgen-paper.Rmd
fix generics insets fig

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.gen.speakerBeliefs %>%
    select(-type, -param, -chain, -Sentence) %>%
    rename(value = val) %>%
    mutate(Parameter = "speakerBeliefs")
)

>>>>

m.gen.speakerBeliefs <- m.samp.prev.params <- m.samp %>%
    filter(type == "targetPrevalence") %>%
    mutate(Sentence = paste(category, property)) %>%
    filter(Sentence %in% example.generics) %>%
    mutate(parameter = paste(param, property, category, sep = "_")) %>%
    select(-param, -property, -category, -chain, -type) %>%
    group_by(parameter) %>%
    mutate(iteration = ave(parameter==parameter, parameter, FUN=cumsum)) %>%
    ungroup() %>%
    separate(parameter, into = c("parameter", "property", "category"), sep= "_") %>%
    group_by(category, property, iteration) %>%
    spread(parameter, val) %>%
    rowwise() %>%
    mutate(
      a = mean*sampleSize,
      b = (1-mean)*sampleSize,
      val = rbeta(n = 1, shape1 = a, shape2 = b)
      ) %>%
    ungroup()

gen.inset.distributions <- bind_rows(
  gen.listener.predictions %>%
    mutate(category = NA),
  m.gen.speakerBeliefs %>%
    select(property, val) %>%
    rename(value = val) %>%
    mutate(Parameter = "speakerBeliefs")
)
